\documentclass[line,lm,rm,11pt]{res} % 10pt is the default, but is way too small

\name{Andrew W. Wagner}
\address{
	%Tiensevest 47, Leuven 3010, Belgium \hspace{1em} cell: 0474 25 82 28 \hspace {1em} email: \texttt{andrew.wagner@esat.kuleuven.be}  
	\begin{ncolumn}{2}
		Tiensevest 47 & email: andrew.wagner@esat.kuleuven.be \\
		  Leuven 3010 & mobile: 0474 25 82 28 \\
			  Belgium & skype: drewm1980
	\end{ncolumn}
}

\renewcommand{\sectionfont}{\sc \LARGE }
\renewcommand{\namefont}{\huge \textbf}
\renewcommand{\labelitemi}{$\diamond$}
\renewcommand{\labelitemii}{$\circ$}

\renewcommand{\resumewidth}{6.5in}
\newsectionwidth{-0.1in}

\def\uiuc{University of Illinois at Urbana-Champaign}
\def\ece{Electrical and Computer Engineering}
\def\eecs{Electrical Engineering and Computer Science}
\def\ge{General Engineering}
\def\bs{\textbf{B.S.}\ }
\def\ms{\textbf{M.S.}\ }
\def\phd{\textbf{Ph.D.}\ }
\def\spaceline{\vspace{1mm} \fullline}

\begin{format}
\title{l}\dates{r}\\
		\employer{l}\location{r}\\
		\body\\
\end{format}

\hyphenation{Wagner}

\begin{document}
\begin{resume}
\vspace{-4mm}
\section{Education}
\begin{itemize}

% PHD 
\item
\spaceline
\employer{\uiuc}
\location{Urbana, IL}

\title{\phd in \ece}
\dates{August 2011}
\begin{position}
\hspace{-00mm}\vspace{-1mm}
{\bf \footnotesize Thesis: Robust and Scalable Face Recognition via Sparse
	Representation and Parallel Programming}
\end{position}

% MS
\item
\title{\ms in \ece}
\dates{December 2006}
\begin{position}
\vspace{-1mm}
{\bf \footnotesize Thesis: Subspace Methods For the Identification Of Hybrid Linear Systems}
\end{position}

%% BA
%\item
%\title{\bs in \ge}
%\dates{May 2003}
%\begin{position}
%Graduated with Honors and a Minor in Mathematics
%\end{position}

\end{itemize}


%\vspace{-3mm}
\section{Employment}
\begin{itemize}
\item
	\spaceline
	\title{\bf Post-Doc Researcher in Airborne Wind Energy }
	\employer{KU Leuven, HIGHWIND Project \\ Supervisor: Prof. Moritz Diehl}
	\location{Leuven, Belgium}
	\dates{Jan. 2012 -- {\bf Mar. 2014}}
	\begin{position}
	\vspace{-2mm}
	\begin{itemize}
		\item Acted as a project coordinator and 3 engineers at the same time (Software, Electrical, and Mechanical)
		\item Designed software and hardware architecture for a prototype power-producing kite plane and launching system.
		\item Rewrote visual tracking system; improved latency by an order of magnitude using O(n) single-pass feature extractor.
		\item Designed a load-bearing tether angle sensor mechanism that can rotate 360 degrees without resorting to sliprings or wireless communication.
		\item Improved development workflow by transitioning the project version control from svn to git and the build system from cmake to tup.
		\item Recruited, trained, and supervised four electrical engineering job students.
		\item Supervised two master's thesis projects.
		\item Taught an undergraduate EE robotics design class.
		%\item Defined and enforced safety precautions that achieved a perfect safety record despite having students working on machinery that is potentially lethal from both mechanical and electrical standpoints.

%(Quadrupled the timing accuracy of signals in our system by triggering the cameras in hardware,
%and installing and tuning priorities of threads in linux with realtime patches.)
%(Wrote a parametric design for a 3D printed multiport air data probe for measuring angle of attack)
%(Optimized the design of a kite launching carousel with dramatically reduced cost and weight)
	\end{itemize}
	\end{position}
\item
	\title{{\bf Ph.D. Researcher in Computer Vision}}
	\employer{University of Illinois, Perception and Decision Lab\\ Advisor: Prof. Yi Ma}
	\location{Urbana, IL, USA}
	\dates{May 2003 -- Oct. 2011}
	\begin{position}
	\vspace{-2mm}
	\begin{itemize}
		\item Designed and Implemented a system for rapidly acquiring images of a person's face under different illuminations, based on a synchronized projector array / camera system.
		\item Implemented L1-Minimization based face recognition system that achieved state of the art recognition performance on unaligned face images with illumination variance and partial occlusions.
		\item Optimized recognition speed via parallelized CPU (OpenMP) and GPU (CUDA) implementations.
		\item Taught an undergrate project-based EE class covering basic analog and digital design.
	\end{itemize}
	\end{position}
%\item
	%\title{\bf Face Recognition Consultant}
	%\employer{Crispin Porter + Bogusky}
	%\location{Boulder, CO, USA}
	%\dates{Jan. 2009 -- Aug. 2009}
	%\begin{position}
	%\vspace{-4mm}
	%\end{position}
%\item
	%\title{\bf Teaching Assistant for ECE110: Introduction to Electrical and Computer Engineering}
	%\employer{University of Illinois at Urbana-Champaign}
	%\location{Urbana, IL, USA}
	%\dates{Jan. 2008 -- Dec. 2008}
	%\begin{position}
	%\vspace{-4mm}
	%\end{position}
\end{itemize}

%\vspace{-3mm}
\section{Skills}
	\begin{itemize}
	\item 
	\spaceline
{\bf Spoken Languages: } English (Chicago Native), French (Intermediate)
\item {\bf Programming Languages: } C, C++, Python, Bash, MATLAB/Simulink, lua
\item {\bf General APIs: } Linux, OpenMP, CUDA, Blas
\item {\bf Specialized APIs: } OpenCV, Orocos, CasADi, ACADO Toolkit
\item {\bf Programming Tools: } Vim, git/svn, clang/gcc/icc, make/CMake/tup, valgrind/gdb
\item {\bf Embedded Platforms: } BeagleBone/ARM, Arduino/Atmel, TI/C6711
\item {\bf Mechanical: } Basic Machining (Mill, Lathe), Laser Cutter, CAD (Rhino, ProE, openscad)
\item {\bf Electrical: } Basic Digital and Analog circuit design, PCB layout/population/rework
\end{itemize}

%\vspace{-3mm}
\section{Research Interests}
\begin{itemize}
\item 
	\spaceline
	{\bf Sensing:} Camera Arrays, Depth cameras, Laser Scanners, IMU Sensor Fusion
\item 
	{\bf Control:} Optimal control of nonlinear systems, Path Planning, State Estimation
\item 
	{\bf Vision:} 3D reconstruction, Optimization based image registration, L1 Minimization/Sparsity
\end{itemize}

%\vspace{-3mm}
\section{Selected Publications}
\begin{itemize}
	\item 
		\spaceline
		Book Chapter: An experimental test setup for advanced estimation and control of an airborne wind energy system. 
		(Kurt Geebelen, Milan Vukov, {\bf Andrew Wagner}, et al. )
		{\it Airborne Wind Energy, Springer, 2013.}
	\item 
		Moving Horizon Estimation with a Huber Penalty Function for Robust Pose Estimation of Tethered Airplanes. 
		(Kurt Geebelen, {\bf Andrew Wagner}, Sebastien Gros, Jan Swevers and Moritz Diehl.) 
		{\it Proc. of the 2013 American Control Conference (ACC), 2013.}
	\item 
		Towards a Practical Face Recognition System: \\Robust Alignment and Illumination by Sparse Representation \\
		({\bf Andrew Wagner}, John Wright, Arvind Ganesh, Hossein Mobahi, Zihan Zhou, Yi Ma) \\
		{ \it IEEE Transactions on Pattern Analysis and Machine Intelligence, 2011. }
\item
		Face Recognition with Contiguous Occlusion using Markov Random Fields \\
			(Zihan Zhou, {\bf Andrew Wagner}, Hossein Mobahi, John Wright, Yi Ma) \\
		{\it Proc. of the IEEE International Conference on Computer Vision (ICCV), 2009.}
	\item Homographies and Matching of Ellipses with Application to Forensic Bloodspatter \\
		Reconstruction 
		(John Wright, {\bf Andrew Wagner}, {Shankar Rao},  Yi Ma) 
		{\it Proc. of the IEEE Conference on Computer Vision and Pattern Recognition (CVPR), 2006.}
	\item Identification of Hybrid Linear Time-Invariant Systems via Subspace Embedding and Segmentation (Kun Huang, {\bf Andrew Wagner}, Yi Ma) {\it Proc. of the IEEE Conference on Decision and Control (CDC), 2004.}
\end{itemize}

\end{resume}
\end{document}
