\documentclass[line]{res}

\name{Andrew W. Wagner}
\address{
	\begin{ncolumn}{2}
	701 W. Washington St. \#1 & cell phone: 312-343-1380 \\
		Urbana, IL 61801 & fax:  217-244-2352 \\ 
		\texttt{http://decision.csl.illinois.edu/$\sim$awagner} &  e-mail: \texttt{awagner@illinois.edu}
	\end{ncolumn}
}

\renewcommand{\sectionfont}{\sc \LARGE }
\renewcommand{\namefont}{\huge \textbf}
\renewcommand{\labelitemi}{$\diamond$}
\renewcommand{\labelitemii}{$\circ$}

%\renewcommand{\resumewidth}{6.7in}
\newsectionwidth{-0.1in}

\def\uiuc{University of Illinois at Urbana-Champaign}
\def\ece{Electrical and Computer Engineering}
\def\cal{University of California at Berkeley}
\def\eecs{Electrical Engineering and Computer Science}
\def\ge{General Engineering}
\def\bs{\textbf{B.S.}\ }
\def\ms{\textbf{M.S.}\ }
\def\phd{\textbf{Ph.D.}\ }
\def\spaceline{\vspace{1mm} \fullline}

\begin{format}
\title{l}\dates{r}\\
		\employer{l}\location{r}\\
		\body\\
		\end{format}

		\hyphenation{Wagner}

		\begin{document}
		\begin{resume}
		\vspace{-2mm}
		\section{Education}
		\begin{itemize}

		% PHD 
		\item
		\spaceline
		\employer{\uiuc}
		\title{\phd cand. in \ece}
		\dates{expected  August 2011}
		\location{Urbana, IL}
		\begin{position}
		\hspace{-00mm}\vspace{-1mm}
{\bf \footnotesize Thesis: Robust and Scalable Face Recognition via Sparse
	Representation and Parallel Programming}
	\end{position}

	% MS
	\item
	\title{\ms in \ece}
	\dates{December 2006}
	\begin{position}
	\vspace{-1mm}
{\bf \footnotesize Thesis: Subspace Methods For the Identification Of Hybrid Linear Systems}
\end{position}

% BA
\item
\employer{\uiuc}
\location{Urbana, IL}
\dates{May 2003}
\title{\bs in \ge \ w/honors: minor in Mathematics}
\begin{position}
\vspace{-3mm}
\end{position}
\end{itemize}

\vspace{-3mm}
\section{Research Interests}
\begin{itemize}
\item 
\spaceline
{\bf Computer Vision:} Face Recognition, Depth Cameras, 3D Reconstruction, Visual Tracking
\item {\bf Control:} Optimal control of nonlinear systems, Path Planning, Hybrid system identification
\item {\bf Power Electronics:} Bi-directional power converters for Alternative Energy.
\end{itemize}

\vspace{-3mm}
\section{Research Experience}
\begin{itemize}
\item
\spaceline
\title{\bf Research Assistant}
\employer{Perception and Decision Laboratory, ECE Dept.}
\location{\uiuc}
\dates{May 2003 -- present}
\begin{position}
Advisor: Professor Yi Ma \\
		\vspace{-6mm}
		\begin{itemize}
\item Designed and implemented a projector-based training acquisition system and robust face recognition system. Implemented Parallel Sparse Representation Solvers (Multi-core, GPU, and Distributed)
	\end{itemize}
	\vspace{-4mm}
	\end{position}
	\end{itemize} 

	\vspace{-2mm}
	\section{Work Experience}
	\begin{itemize}
	\item
	\spaceline
	\title{\bf Face Recognition Consulting}
	\employer{Crispin Porter + Bogusky}
	\location{Boulder, CO}
	\dates{Jan. 2009 -- Aug. 2009}
	\begin{position}
	%Advisor: Terrence Curran \\
		\vspace{-4mm}
		\end{position}
	\item
	\title{\bf Teaching Assistant for ECE110: Introduction to Electrical and Computer Engineering}
	\employer{University of Illinois at Urbana-Champaign}
	\location{Urbana, Illinois}
	\dates{Jan. 2008 -- Dec. 2008}
	\begin{position}
		\vspace{-4mm}
		\end{position}
		\end{itemize}


		\vspace{-3mm}
		\section{Selected Publications}
		\begin{itemize}
		\item 
		\spaceline
Towards a Practical Face Recognition System: \\Robust Alignment and Illumination by Sparse Representation \\
		({\bf Andrew Wagner}, John Wright, Arvind Ganesh, Hossein Mobahi, Zihan Zhou, Yi Ma) \\
{ \it IEEE Transactions on Pattern Analysis and Machine Intelligence, 2011. (under review) }
\item
		Face Recognition with Contiguous Occlusion using Markov Random Fields \\
			(Zihan Zhou, {\bf Andrew Wagner}, Hossein Mobahi, John Wright, Yi Ma) \\
{\it Proc. of the IEEE International Conference on Computer Vision (ICCV), 2009.}
\item Towards a Practical Face Recognition: Robust Pose and Illumination via Sparse Representation \\
		({\bf Andrew Wagner}, John Wright, Arvind Ganesh, Zihan Zhou, Yi Ma) \\
{ \it Proc. of the IEEE Conference on Computer Vision and Pattern Recognition (CVPR), 2009. }
%\item The Algebra and Statistics of Generalized Principal Component Analysis 
% ({Shankar Rao}, Harm Derksen, Robert Fossum, Yi Ma, { Andrew Wagner}, Allen Yang) {\it Proc. of the VCIP Special Session on the Mathematics of Imaging, 2007.}
\item Homographies and Matching of Ellipses with Application to Forensic Bloodspatter \\
	Reconstruction 
(John Wright, {\bf Andrew Wagner}, {Shankar Rao},  Yi Ma) 
{\it Proc. of the IEEE Conference on Computer Vision and Pattern Recognition (CVPR), 2006.}
\item Segmentation of Hybrid Motions via Hybrid Quadratic Surface Analysis ({Shankar Rao}, {\bf Andrew Wagner}, Allen Yang, Yi Ma) {\it Proc. of the International Conference on Computer Vision (ICCV), 2005.}
%\item Hilbert Functions and Applications to the Estimation of Subspace Arrangements (Allen Yang, {Shankar Rao}, %{\bf Andrew Wagner}, Robert Fossum, Yi Ma) {\it Proc. of the International Conference on Computer Vision (ICCV), 2005.}
%\item Segmentation of a Piece-Wise Planar Scene from Perspective Images (Allen Yang, {Shankar Rao}, { Andrew Wagner}, Yi Ma) {\it Proc. of the IEEE Conference on Computer Vision and Pattern Recognition (CVPR), 2005.}
\item Identification of Hybrid Linear Time-Invariant Systems via Subspace Embedding and Segmentation (Kun Huang, {\bf Andrew Wagner}, Yi Ma) {\it Proc. of the IEEE Conference on Decision and Control (CDC), 2004.}

\end{itemize}


	% \item
	% \title{\textbf{Teaching Assistant}}
	% \employer{ECE Dept.}
	% \location{\uiuc}
	% \dates{August 2001 -- present}
	% \begin{position} 
%Courses Taught: Artificial Intelligence (ECE 448), Digital Signal Processing (ECE 410), Biomedical Instrumentation (ECE 414/415)
	%\end{position}


	\vspace{-3mm}
	\section{Selected Coursework}
	\begin{itemize}
	\item 
	\spaceline
% Spring 2003
ECE 449: Computer Vision (A)	
% Fall 2003
ECE 310: Digital Signal Processing (B+)
ECE 313: Probability \& Applications (B+)
ECE 415: Control System Theory and Design (B+)

% Spring 2004
ECE 451: Digital Signal Processing (B)
GE 493: Special Problems (A)

% Summer 2004
ECE 340: Solid State Electronic Devices (B-)
ECE 350: Lines, Fields, and Waves (B)

% Fall 2004
ECE 442: Electronic Circuits (B-)
ECE 598: Special Topics in ECE (A)

% Spring 2005
ECE 528: Analysys of Nonlinear Systems (A-)
ECE 550: Advanced Robotic Planning (B)

% Fall 2005
ECE 520: Electromagnetic Waves and Radiating Systems (A-)
ECE 547: Image Processing

% Spring 2006
ECE 490: Introduction to Optimization (B)
ECE 586: Topics in Decision and Control (A)

% Spring 2007
ECE 553: Optimum Control Systems (B)
ECE 558: Digital Imaging (A)

% Fall 2007
ECE 464: Power Electronics (B-)
ECE 410: Power Electronics Lab (B)


	\end{itemize}

	\vspace{-3mm}
	\section{Skills}
	\begin{itemize}
	\item 
	\spaceline
{\bf Programming Languages: } C, C++, C for CUDA, Python/Numpy, Matlab, Bash, Latex, Asymptote
\item {\bf Programming API's: } OpenCV, BLAS (MKL, uBlas, Eigen), OpenMP, Pthreads
\item {\bf Other: } Atmel Microcontrollers, TI DSPs, Electronics Design/Rework, Rhino CAD, Basic Machining
\end{itemize}

		\end{resume}
		\end{document}
