% Cover letter using letter.cls
\documentclass[11pt]{letter} % default is 10 pt
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page
\textheight=8.5in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}


\signature{Andrew Wagner}                  % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
\begin{letter}{Mr. Andrew Wagner \\
Post-Doc Researcher \\
KU Levuen \\
Heverlee, Belgium 3010} 

%\begin{center}
%\large\bf ANDREW J. MALONE \\
%739 Mill Grove Drive \\ Audubon, PA 19403 \\ (215) 555-2216
%\end{center} 
\vfill % forces letterhead to top of page

\opening{Dear Makani Team Leaders:} 
 
\noindent Thank you for taking the time to consider my application.  I am
currently working for Moritz Diehl as a Post-Doc researcher on the HIGHWIND
Airborne Wind Energy project at the University of Leuven, Belgium, and am
seeking a full-time position in the AWE industry. I have met Corwin, and later,
Damon during their visits to Leuven while they acted as members of our
Scientific Advisory Board. Additionally, I have worked with former Makani
associates Greg Horn and Pranay Sinha, so needless to say, I am well versed in
the challenges facing AWE, and excited about the progress your team has made
towards a commercially viable system.  

\noindent Within the HIGHWIND project, we have been developing algorithms and
software toolkits for real-time optimal control, as well as prototyping a
carousel-based launching system for pumping-mode AWE systems.  In addition to
being the main coordinator and supervisor for our small team of Ph.D's working
on flight experiments, I have personally performed electrical, mechanical, and
software engineering for the project.  

During the first year of my stay I 
leveraged my background in computer vision to improve the speed and tracking
performance of the vision system we use to track kites.  For the second year,
the project I am most proud of was the mechanical and electrical development of
a load bearing line angle sensor for the mobile/outdoor experimental setup we
are developing.  

\noindent I am available to meet over skype (username drewm1980).  I would also
love to visit in person, meet you all, and see the company.  While I am
currently living in Belgium, I am a US native willing to relocate back home.
Thank you for taking the time to consider my credentials.
 
\closing{Sincerely yours,}
 
\encl{}

\end{letter}
 

\end{document}




